Adopting agile in the large: motivations, success factors and challenges

### 2014-05-12 journal/article.tex
Problems with HR

@@

Problems in adopting agile were even showing in functions outside the software
delivery lifecycle. A support function that was particularly mentioned to
have issues in agile adoption was human resouces (HR).

>>>>

% Problems with HR

Problems in adopting agile were even showing in functions outside the software
delivery lifecycle. In several cases human resouces (HR) was a support function
mentioned to work against the agile adoption. In order to gain full results of
the transformation the entire organization should to be aligned, including HR
[P38, P42, P49].
Especially the rewarding practices set by HR were seen as problematic for the
agile model. Rewarding was tied to personal performance, which was acting
against team centric thinking and the agile model in general [P3, P6, P49].
One case reported even on a practice of tracking failures down to individuals
[P40].

@@
